Cytoplasm Simulation

### 2019-09-10 paper/virtual_cytoplasm_v2.tex
small correction
barplot script added to make hb sasa rmsd plots. some plots added as pdf. Makefile
diff data added
diff plots added and manuscript updated

\subsubsection{Aggregation}
We observed aggregation of the metabolites that contain phosphate, ATP and FBP, with Mg2+ that was used as initially used as counter-ion for ATP and tRNA. After running simulations of small boxes containing just these metabolites and Mg2+, we found that completely protonating their phosphate groups can prevent aggregation. Thus, we advise caution when dealing with small molecules that are highly charged, such as ATP and FBP. Trial simulations with small boxes in which these metabolites are in high concentration to verify if they'll aggregate with Mg2+ or other charged species that are present in the box. In the specific case of ATP and FBP modeled with GAFF in boxes containing Mg2+, we advise that they should be completely protonated even though that is not their physiological protonation state.

@@

>>>>

\begin{figure}
\includegraphics[scale=0.6]{diff_singles.pdf} &
\includegraphics[scale=0.6]{diff_cyto.pdf} &
\includegraphics[scale=0.6]{diff_cyto_over_singles.pdf}
\caption{A) Diffusion coefficient of crowders from single molecule simulations.  B) Diffusion coefficient of crowders from cytoplasm simulations. C) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{rmsd.pdf}
\caption{Root mean squared displacement of 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars).}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{sasa.pdf}
\caption{Solvent accessible surface area of 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars).}

\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{rmsf.pdf}
\caption{Root mean squared fluctuations of 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues of each chain of crowders.}
\end{figure}

\subsubsection{Olygomers under crowded condition}
\begin{figure}
\includegraphics[scale=0.6]{hb.pdf}
\caption{Intramolecular hydrogen bonds for crowders that appear as olygomers from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The cytoplasm data are not correct!}
\end{figure}

\subsubsection{Aggregation}
We observed aggregation of the metabolites that contain phosphate, ATP and FBP, with Mg2+ that was used as initially used as counter-ion for ATP and tRNA. After running simulations of small boxes containing just these metabolites and Mg2+, we found that completely protonating their phosphate groups can prevent aggregation. Thus, we advise caution when dealing with small molecules that are highly charged, such as ATP and FBP. Trial simulations with small boxes in which these metabolites are in high concentration to verify if they'll aggregate with Mg2+ or other charged species that are present in the box. In the specific case of ATP and FBP modeled with GAFF in boxes containing Mg2+, we advise that they should be completely protonated even though that is not their physiological protonation state. The topology and structure files we are providing for ATP and FBP on github are already protonated.

@@

\begin{figure}
\includegraphics[scale=0.6]{rdf_RNA_metabolites.pdf}
\caption{Radial distribution function showing the probability of finding a metabolite around RNA molecules.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{avclust.pdf}
\caption{Number of metabolite molecules that form a cluster in cytoplasm simulations.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{nclust.pdf}
\caption{Number of clusters that form during the cytoplasm simulations.}
\end{figure}
